---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# visualPlots R package

<!-- badges: start -->
<!-- badges: end -->

visualPlots is an R package that provides tools for creating visualizations. It is designed to be easy to use and flexible, allowing 
users to create a wide variety of plots and charts from quantitative and qualitative data. The package includes functions for creating 
scatter plots, line graphs, bar charts, and more, as well as tools for customizing the appearance of your plots.

## Installation

You can install the development version of visualPlots like so:

``` {r}
# devtools::install_github("jumagari14/visualRPlots")
```

## Example

You can find below examples of basic visualizations that can be created using the visualPlots package. For more detailed examples and documentation, 
please refer to the package's GitHub repository.:

### Boxplots comparing quantitative data across groups + statistical test
```{r}
# library(visualPlots)
data(iris)
irisDataPlot <- plot_boxplot_stats(data = iris, x = "Species", y = "Sepal.Length",
                           parametric = TRUE, add_points = TRUE,color_palette="Set3",
                           show_symbols = TRUE, show_posthoc = TRUE)
print(irisDataPlot$plot)

```
### Scatter plot with regression line and confidence interval
```{r}
# library(visualPlots)
data(iris)
plot_correlation(data = iris, x = "Sepal.Length", y = "Petal.Length", 
                cor_method = "pearson")
```
### Bar plot with error bars
```{r}
# library(visualPlots)
data(mtcars)
plot_stacked_bar(data = mtcars, x = "cyl", fill = "am", 
                color_palette="Set2")
```

